Ants-Review: an Ethereum-Based Privacy-Oriented Protocol for Incentivized Open Peer Reviews

### 2020-12-24 article.tex
Prova: update affiliations but the title is suppressed because it's too long

\author{Bianca Trovò\inst{1}\orcidID{0000-0002-6776-2304}\thanks{Corresponding author}\and
Nazzareno Massari\inst{2}\orcidID{0000-0002-6638-2174}\thanks{The two authors contributed equally to this work}}

@@

\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, Paris, France

@@

\and MakerDAO, Community Development, London, United Kingdom \\

@@

Besides a growing number of applications ranging from De-Fi, healthcare, music industry, government, identity, to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a `game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}. Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} in which decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers). Those are: the consensus algorithm \cite{ConsAlg}, a deterministic computational trust that allows for \emph{decentralization}, for which there are no trusted third parties; the proof of existence (PoE) that via \emph{cryptographic hashing} and \emph{timestamping} creates a digital footprint able to keep a traceable chronological record of research objects that cannot be altered or retrieved (due to its property of \emph{immutability} or \emph{append-only})\cite{ReviewBlockchain2019}. In particular, a `blockchainified science'\cite{BlockchainforScience} could `reduce waste'\cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to `scientific self-correction' way before the final publication step, and therefore help fixing the current reproducibility crisis in science.

@@

\subsubsection{Transparency and re-usability of the records.} The peer review history, including reviewers' recommendations and authors' replies, should be openly and permanently accessible to the community (in the form of `open reports' of open peer reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge. Following the example of models offered by journals peer review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[4]{\emph{Neuroscience Peer Review Consortium}. http://nprc.incf.org} and independent companies like \emph{ResearchSquare} \footnote[5]{\emph{ResearchSquare}. https://www.researchsquare.com} and \emph{Peerage of Science} \footnote[6]{\emph{Peerage of Science}.  https://www.peerageofscience.org}, that provide a scientific peer review service, peer reviews in Ants-Review will be transferable across journals (like in `cascading' or `portable peer reviews').

@@

\subsubsection{Supplementary Material}
Source code, DOI: 10.5281/zenodo.3971044; DApp: https://ants-review.on.fleek.co.

>>>>

\author{Bianca Trovò\inst{1,2}\orcidID{0000-0002-6776-2304}\thanks{Corresponding author}\and
Nazzareno Massari\inst{3,4}\orcidID{0000-0002-6638-2174}\thanks{The two authors contributed equally to this work}}

@@

\institute{Sorbonne Université, Faculté des Sciences et Ingénierie, Paris, France \and
Atomic Energy and Alternative Energies Commission (CEA), Frédéric Joliot Institute for Life Sciences, NeuroSpin, UNICOG, INSERM U992, Paris-Saclay, France

@@

\and MakerDAO, Community Development, London, United Kingdom \and
WFIL Labs\\

@@

Besides a growing number of applications ranging from De-Fi, healthcare, music industry, government, identity, to cite but a few, blockchain technology has recently started to catalyse the attention of the scientific community as well \cite{Bitcoin-Nature-focus,vanRossum2017-DigSci} with the promising potential of being a `game changer' in outdated and broken scientific practices and leading towards open science \cite{AES}. Indeed, scholars have pointed out how the intrinsic characteristics of blockchain technology set the basis for a open science infrastructure \cite{ReviewBlockchain2019} in which decisional processes are transparent and therefore more democratically accessible to all the stakeholders (researchers, reviewers, funders, taxpayers). Those are: the consensus algorithm \cite{ConsAlg}, a deterministic computational trust that allows for \emph{decentralization}, for which there are no trusted third parties; the proof of existence (PoE) that via \emph{cryptographic hashing} and \emph{timestamping} creates a digital footprint able to keep a traceable chronological record of research objects that cannot be altered or retrieved (due to its property of \emph{immutability} or \emph{append-only}) \cite{ReviewBlockchain2019}. In particular, a `blockchainified science' \cite{BlockchainforScience} could `reduce waste' \cite{ReducingWaste-Lancet}, by disclosing each step in the research cycle to `scientific self-correction' way before the final publication step, and therefore help fixing the current reproducibility crisis in science.

@@

\subsubsection{Transparency and re-usability of the records.} The peer review history, including reviewers' recommendations and authors' replies, should be openly and permanently accessible to the community (in the form of `open reports' of open peer reviews) even before articles' publication in order to  make editorial decisions more democratic and prevent waste of knowledge. Following the example of models offered by journals peer review consortia, such as the \emph{Neuroscience Peer Review Consortium}\footnote[4]{\emph{Neuroscience Peer Review Consortium}. http://nprc.incf.org} and independent companies like \emph{ResearchSquare}\footnote[5]{\emph{ResearchSquare}. https://www.researchsquare.com} and \emph{Peerage of Science}\footnote[6]{\emph{Peerage of Science}.  https://www.peerageofscience.org}, that provide a scientific peer review service, peer reviews in Ants-Review will be transferable across journals (like in `cascading' or `portable peer reviews').

@@

\subsubsection{Supplementary Material}
Source code, DOI: 10.5281/zenodo.3971044;DApp: https://ants-review.on.fleek.co.
